Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-28 paper/ms.tex
almost done with section 4

\begin{figure}
\begin{center}
\includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
\caption{ \label{fig:laes_dist} Surface density of dark
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents on of the
  $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
  in the Bolshoi simulation. The horizontal grey band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure}

@@

In Figure \ref{fig:laes_dist} we present the results for  the
integrated dark matter halo surface density as a function of halo
mass. Each line corresponds to one of the 210 sub-volumes in the
Bolshoi simulation. The gray band indicates the surface density
values for LAEs allowed reported in observations \citep{Yamada2012}.

This result provides the basis to understand why a range of models
${\mathcal M}$ can be expected to be consistent with
observations. In Figure \ref{fig:laes_dist} we can read that models
with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
surface number density lower than the observational
constrain. The oppossite is true in models with $\log_{10} M_{\rm min}<10.5$
that will show surface number density larger than observations, this
implies that in such models the occupation fraction has to be tuned
$f_{\rm occ}<1.0$ as to lower the halo numeber density to match the
gray band values.

@@

The upper (lower) panels correspond to the {\texttt match} ({\texttt
  random}) method to build the mock surveys from individual
fields. The color code shows the number of mock surveys consistent
with observations. In both cases there are three regions of parameter
space that can be clearly distinguised.

The first region corresponds to models where the minimum mass is high
$\log_{10}M_{\rm min}> 11.5$. None of this models is compatible with
observations as expected from the results in the previous section. For
these models the number density of LAEs is too low.

@@

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
\end{center} 
\caption{ Number of models with a mininium number of mock survey
  realizations that are consistent with observations.
  \label{figure:high_success_rate}.}  
\end{figure*}

The raw results of our experiments yield a prefered range for
halo masses hosting LAES bounded by a minimum mass $10^{10}\hMsun<M_{\rm
  min}<10^{11.5}\hMsun$ and without any limitation on the  maximum
mass. In this regime the average occupation fraction varies with an
approximate dependence of the kind $f_{occ}\approx 0.1 (M_{\rm
  min}/10^{10})^{XX}$. These results discard models that were
nevertheless disfavored from the very beginning based on the results
of the mass functions (see Figure 1.).

In this section we consider three different ways to impose
tighter constraints on this mass range by making use of the results we
have derived so far together with additional statistical and
astrophysical constraints. In the first constraint we select the
models where all the mock surveys present KS-test values consistent
with observations. The second constraints uses recent observational
results on the average occupation fraction for LAEs at high-z. The
third exploits the information in the Angular Correlation Function
(ACF).

\subsubsection{Models with the highest success rates}

For each model there are 15 different mock survey realizations. In the
previous section we presented the models that had at least one (1)
mock survey realization with $P>0.05$.

In Figure \ref{figure:high_success_rate} we show the number of models
that have at least $n$ realizations with $P>0.05$ for the {\texttt
  match} and {\texttt random} methods.  This shows that there are
around $550$ to $600$ different models that have at leaset one mock
survey realization consistent with observations. At the other extreme,
there are $80$ to $100$ models with all the 15 realizations with
$P>0.05$. Here we focuse on the latter models. The best models
represent $\sim 15\%$ of the number of initially considered good
models.

In Figure XX we present the locii of these models in the parameter
space $M_{\rm min}-M_{\rm max}$ and $M_{\rm min}-f_{\rm occ}$. In
Figure XX we show the spatial distribution for two mock surveys
corresponding to one of such models.

\subsubsection{Observational constraints on the occupation fraction}

We now impose a different restriction using the observational results
by \cite{Hayes2010}. These authors constrained the value of $f_{\rm
  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
on blind surveys of the H$\alpha$ and Lyman alpha line with the European Southern
Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
esc}=(10.7\pm 2.8)$ if a different dust correction is used. The
authors show that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman-alpha to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$.

For the cosmological parameters used in this \documentname the age of
the universe between $z=3.1$ and $z=2.2$ has changed by $\sim 1$
Gyr. We assume that the physical conditions that determine the escape
fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm  occ}$
remain constant over that time scale. This assumption allows us to
further pick models that have an occupation fraction of $f_{\rm
  occ}=0.10$. Under this selection only $18$ models can
beselected. Considering an occupation fraction $f_{\rm occ}=0.20$
another $39$ models can beconsidered. This constraint help us to
select $\sim 10\%$ of theoriginal models that were considered as
consistent with observations in the previous section.

Figure XX shows the prefered models in the planes $M_{\rm min}-M_{\rm
  max}$ and $M_{\rm min}-f_{\rm occ}$ for the {\tt match} and {\tt
  random} methods. The list for the model parameters is found in the
appendix in Table XX.

In terms of the constraints done in the previous sub-section, we find
that the models in this region of parameter space have an average
number of XX mock catalogs consistent with observations.

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
\end{center} 
\caption{Favored models when the constraints on the maximal number of
  consistent mocks and the observational constrain on the occupation
  fraction are included.
  \label{figure:mock_and_f_occ}}  
\end{figure*}

\subsubsection{Constraints from the Angular Correlation Function}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
\end{center} 
\caption{Spatial distribution for two mocks corresponding to the model
  $M_{\rm min}=$, $M_{\rm max}=$ and $f_{\rm occ}=$. All the 15
  different mock  surveys for this model in the {\texttt match}
  configuration are consistent with observations at the $P>0.05$
  level. The full data for all the mocks can be found in the github
  repository for this paper.
  \label{figure:spatial_distro}.}
\end{figure*}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
\caption{ \label{fig:halos} Surface density of dark
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents on of the
  $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
  in the Bolshoi simulation. The horizontal grey band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure}

@@

In Figure \ref{fig:halos} we present the results for  the
integrated dark matter halo surface density as a function of halo
mass. Each line corresponds to one of the 210 sub-volumes in the
Bolshoi simulation. The gray band indicates the surface density
values for LAEs allowed reported in observations \citep{Yamada2012}.

This result provides the basis to understand why a range of models
${\mathcal M}$ can be expected to be consistent with
observations. In Figure \ref{fig:halos} we can read that models
with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
surface number density lower than the observational
constrain. The oppossite is true in models with $\log_{10} M_{\rm min}<10.5$
that will show surface number density larger than observations, this
implies that in such models the occupation fraction has to be tuned
$f_{\rm occ}<1.0$ as to lower the halo numeber density to match the
gray band values.

@@

The upper (lower) panels correspond to the {\texttt match} ({\texttt
  random}) method to build the mock surveys from individual
fields. The plot shows number of mock surveys consistent
with observations. There are between $550$ to $600$ models out of the
original $9000$ models that have at least one (1) mock survey
consistent with observations.

In Figure \ref{fig:landscale} there are three regions of parameter
space that can be clearly distinguised. The first region corresponds
to models where the minimum mass is high $\log_{10}M_{\rm min}>
11.5$. None of this models is compatible with observations as expected
from the results in the previous section. For these models the number
density of LAEs is too low.

@@

Without any additional information our method allows us to infer that
most of the succesful models are found in the second and third region of
parameter space where. This result was already expected from halo
abundance calculations shown in Figure \ref{fig:halos}. In the next
section we reduce the size of this region by using more stringent
constraints to define the agreement with observations and including
additional observational information onpossible values for the
occupation fraction at $z\sim 3$.

%The raw results of our experiments yield a prefered range for
%halo masses hosting LAES bounded by a minimum mass $10.5<\log_{10}M_{\rm
%  min}<11.5$ and without any limitation on the  maximum
%mass. In this regime the average occupation fraction tends to increase
%with $M_{\rm min}$. These results discard models that were
%nevertheless disfavored from the very beginning based on the results
%of the mass functions (see Figure 1.).

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
\end{center} 
\caption{ Number of models with a mininium number of mock survey
  realizations that are consistent with observations.
  \label{fig:high_success_rate}.}  
\end{figure*}

In this section we consider two additional constraints on the models
we accept as succesul. First by taking models with the
highest possible number of mock surveys consistent with
observations. Second by including additional observational constraints
on the occupation fraction for high redshift LAEs.

%In this section we consider three different ways to impose
%tighter constraints on this mass range by making use of the results we
%have derived so far together with additional statistical and
%astrophysical constraints. In the first constraint we select the
%models where all the mock surveys present KS-test values consistent
%with observations. The second constraints uses recent observational
%results on the average occupation fraction for LAEs at high-z. The
%third exploits the information in the Angular Correlation Function
%(ACF).

\subsection{Models with the highest success rates}

For each model ${\mathcal M}$there are 15 different mock surveys. In the
previous section we presented the models that had at least one (1)
mock survey with $P>0.05$.

Figure \ref{fig:high_success_rate} shows the number of models
that have at least $N_{\rm high-P}$ mocks with $P>0.05$ for the {\texttt
  match} and {\texttt random} methods.  This shows that there are
here are between $80$ to $100$ models with all the 15 realizations with
$P>0.05$. This a reduction of a factor of $\sim 6$ with repect to the
total number of mocks with at least one consistent mock. 
%Here we focuse on the latter models. 
%The best models
%represent $\sim 15\%$ of the number of initially considered good
%models.

Figure \ref{fig:restriction_mock} presents the locii of these models
in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
  min}-f_{\rm occ}$ for the {\texttt match} method, the results for
the {\texttt random} method are similar. In this case the models with
$\log_{10}M_{\rm min}< 11.7$ are greatly reduced. This corresponds to
the regions in the parameter space in Figure \ref{fig:landscape} that
already had a low number of consistent mock surveys. From the right
panel in Figure \ref{fig:restriction_mock} one can see that there is
not a strong selection effect on the occupation fraction $f_{\rm
  occ}$.

\subsection{Observational constraints on the occupation fraction}

We impose a different restriction using the observational results
by \cite{Hayes2010}. These authors constrained the value of $f_{\rm
  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the European Southern
Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
esc}=(10.7\pm 2.8)$ if a different dust correction is used. The
authors show that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$.

For the cosmological parameters used in this \documentname the age of
the universe between $z=3.1$ and $z=2.2$ has changed by $\sim 1$
Gyr. We assume that the physical conditions that determine the escape
fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm  occ}$
remain constant over that time scale. We limits the escape fraction to
be in the range further pick models that have an occupation fraction of $f_{\rm
  occ}\leq 0.2$ to allow for some flexibility. With this additional
constraint between $35$ to $40$ models are consistent with
observations. 
%Considering an occupation fraction $f_{\rm occ}=0.20$
%another $39$This constraint help us to
%select $\sim 10\%$ of theoriginal models that were considered as
%consistent with observations in the previous section.

Figure  \ref{fig:restriction_mock_and_f_occ}   shows the prefered
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random}
methods. The list for the parameters in these models is found in the appendix in
Table XX.

%In terms of the constraints done in the previous sub-section, we find
%that the models in this region of parameter space have an average
%number of XX mock catalogs consistent with observations.

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_f_occ_mock.pdf}
\end{center} 
\caption{Favored regions in parameter space when the constraints on
  the maximal number of consistent mocks is imposed. The results for
  the {\texttt random} methodology area very similar to the ones
  presented here for the {\texttt match} method.
  \label{fig:restriction_mock}}  
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
\end{center} 
\caption{Favored models when the constraints on the maximal number of
  consistent mocks and the observational constrain on the occupation
  fraction are included.
  \label{fig:restriction_mock_and_f_occ}}  
\end{figure*}

\section{Results for the Angular Correlation Function}

@@

%\begin{figure*}
%\begin{center}
%\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
%\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
%\end{center} 
%\caption{Spatial distribution for two mocks corresponding to the model
%  $M_{\rm min}=$, $M_{\rm max}=$ and $f_{\rm occ}=$. All the 15
%  different mock  surveys for this model in the {\texttt match}
%  configuration are consistent with observations at the $P>0.05$
%  level. The full data for all the mocks can be found in the github
%  repository for this paper.
%  \label{figure:spatial_distro}.}
%\end{figure*}
